% Resume in Latex
% Author : Bently Metayer

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% -------------------- HEADING --------------------
\begin{center}
    \textbf{\Huge \scshape Bently Metayer} \\
    \small 
    \faIcon{github} \href{https://github.com/bentlym}{\underline{github.com/bentlym}} 
        \faIcon{globe} \href{https://bentlym.github.io/portfolio/}{\underline{bentlym.github.io/portfolio}} \quad\faIcon{linkedin} \href{https://www.linkedin.com/in/BentleyMetayer}{\underline{linkedin.com/in/BentlyMetayer}} \quad
    \end{center}

% -------------------- SUMMARY --------------------
\section{Summary}
\resumeSubHeadingListStart
    \item{
        Systems Engineer and Full Stack Developer focused on high-performance infrastructure, CLI tooling, and Unix-based systems. Expert in bridging high-level application logic (Python, TypeScript) with low-level systems programming (Rust/C++) to build scalable, production-grade software.
    }
\resumeSubHeadingListEnd

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Broward College}{Fort Lauderdale, FL}
      {A.A. / A.S. in Computer Science (in progress) $|$ \emph{Aspiring University of Florida Transfer}}{Expected 2027}
  \resumeSubHeadingListEnd

% -------------------- TECHNICAL SKILLS --------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
     \item \textbf{Languages}{: C++, Rust, Python, TypeScript, JavaScript (ES6+), SQL, Shell Scripting}
     \item \textbf{Trading \& Systems}{: Interactive Brokers API, Order Routing, Market Data Streaming, WebSockets}
     \item \textbf{Development}{: Linux/Unix, CLI Tooling, GNOME Extensions, Docker, Git, CI/CD, Makefile, Turborepo}
     \item \textbf{Web \& Backend}{: Node.js, Actix, PostgreSQL, SQLite, Next.js, RESTful APIs, System Design, Tokio, Ratatui, Plotters, SQLx}
    }
 \end{itemize}

% -------------------- EXPERIENCE & PROJECTS --------------------
\section{Projects \& Experience}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Rustiq (RSTQ)} $|$ \emph{Rust, Tokio, Ratatui, SQLx}}{2026 -- Present}
      \resumeItemListStart
        \resumeItem{Engineered an asynchronous data pipeline using Tokio and Reqwest for low-latency market data ingestion.}
        \resumeItem{Improved performance optimization and reliability of caching systems by 25\% through SQLx and SQLite data modeling.}
        \resumeItem{Developed and maintained high-quality, scalable terminal interfaces (TUI) using Ratatui and Plotters.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Algo Trading CLI} $|$ \emph{TypeScript, Node.js, Rust}}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Architected a command-line interface for automated trade settlement and decentralized portfolio management.}
        \resumeItem{Improved performance and reliability of trading systems by 20\% through optimization and caching strategies.}
      \resumeItemListEnd



    \resumeProjectHeading
      {\textbf{Gridnews} $|$ \emph{TypeScript, Next.js, Node.js, PostgreSQL, Rust}}{2024 -- Present}
      \resumeItemListStart
        \resumeItem{Designed a scalable news aggregation platform using a grid-based UI and a high-concurrency Rust backend.}
        \resumeItem{Developed and maintained high-quality, scalable backend services using TypeScript, Node.js, and PostgreSQL.}
        \resumeItem{Improved system scalability by 40\% through efficient resource allocation and containerized Docker environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% -------------------- OPEN SOURCE & COMMUNITY --------------------
\section{Open Source \& Achievements}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Stoqey/IBKR (Contributor)} $|$ \emph{TypeScript}}{2025}
      \resumeItemListStart
        \resumeItem{Authored comprehensive technical documentation for order configuration, clarifying Interactive Brokers API integrations for institutional-grade routing.}
        \resumeItem{Improved developer experience by standardizing code snippets and detailing critical execution parameters including Time-in-Force (TIF) and After-Hours trading (outsideRth).}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{public-apis/public-apis (Contributor)}}{2026}
      \resumeItemListStart
        \resumeItem{Added the GridNews API to the curated list of free public APIs to promote open financial data.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{vinegarhq/sober (Contributor)}}{2026}
      \resumeItemListStart
        \resumeItem{Troubleshot and documented Linux Vulkan-specific crashes on NVIDIA driver setups for a Roblox runtime.}
        \resumeItem{Collaborated with cross-functional open-source teams to identify and prioritize technical debt.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{gorilla-devs/ferium (Contributor)} $|$ \emph{Rust}}{2024}
      \resumeItemListStart
        \resumeItem{Participated in open-source discussions, issue reporting, and tracking for the CLI Minecraft mod manager written in Rust.}
        \resumeItem{Improved code quality and reduced bugs through active feedback and issue tracking.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}